Outline--Draft JCP format for: Reactive Force Field for Solid Oxides Containing Lanthanum

### 2019-05-24 Paper/paper.tex
Update paper.tex
Cleaned up some lines
Updated abstract
Changed abstract to be more in line with intended study of La

Conversion of CO2 to syngas can be achieved in solid oxide electrolysis cells at high temperatures (~1000 K) by using Perovskite-based solid oxides as electrocatalysts. This process is projected to be a viable way of generating fuels by converting, and therefore reducing, CO2 from industrial emissions. However, full understanding of the mechanism involved in CO2 conversion on these electrocatalysts is far from complete. In this work, we perform DFT calculations and reactive molecular dynamics to understand the electronic structure and stability of perovskite-based solid oxides used as electrocatalysts for CO2 conversion. To this end, our study involves firstly, generation of a dataset from DFT calculations, which include optimized geometries, equations of state, surface energies, and slab—CO2 interactions from a set of ABO3-type perovskites. Secondly, we parametrize the reactive force field, ReaxFF, using an annealing Monte Carlo optimizer and a covariance matrix adaptation evolution strategy. Finally, we explore bulk dynamics of the perovskites at high temperature and the time evolution of reactions involving CO2 on the surface of slabs from the perovskites. Of interest, our results demonstrate the modes in which the CO2 is chemisorbed at high temperature; the consequent formation of intermediates; and their role in further conversion of the CO2. This study serves as a base to elucidate the elementary steps involved in the mechanism of CO2 conversion on perovskites at high temperature, which will allow us to understand the most favorable conditions for the reaction to occur and, consequently, provide us of a way to improve the design of perovskite-based solid oxide electrocatalysts.
\end{abstract}

>>>>

In this work, we perform the parametrization of a reactive force field, ReaxFF, for Lanthanum and its oxides.
We describe the procedure followed and provide results that validate the derived parameters in their ability to describe bulk structures, surfaces, and nanoparticles.
Comparison of our results using ReaxFF and electronic structure methods show good agreement in the reproduction of surfaces energies and bulk modulus; with the latter showing good agreement with experimentally reported results.
We also show that our parametrization is able to capture the trend in adsorption energies between Lanthanum oxides and adsorbates like methane and water \textbf{to be obtained}.
These results highlight the utility of ReaxFF to study systems containing Lanthanum and provide a significant addition to reactive molecular dynamics for studying properties and even redox properties on Lanthanum oxide surfaces.

\end{abstract}
